Detecting Facial Expressions in Professional Tennis Matches

### 2017-09-19 Report06-12.Rmd
Remove numbers from some sections

---
title: "Detecting Facial Expressions in Professional Tennis Matches"
author: "Stephanie Kobakian, Mitchell O'Hara-Wild, Dianne Cook, Stephanie Kovalchik"
date: "28 July 2017"
output: bookdown::pdf_document2
number_sections: false
toc: false
fig_caption: yes
fontsize: 11pt
documentclass: article
bibliography: references.bib
biblio-style: apalike
link-citations: true
---

@@

#Abstract

@@

##Software Selection
The choice of the initial software considered for this research was informed by a report that reviewed 'commercial off-the-shelf (COTS) solutions and related patents for face recognition in video surveillance applications.' [@Survey]

@@

##Manual Annotation
To record the details of attributes for each face and scene a Shiny [@shiny] App was created. We called this Application our ManualClassificationProgram. This helped to provide information for all attributes quickly and consistently.

@@

```{r Image-Characteristics-Table, fig.cap ="\\label{tab:Image-Characteristics-Table}"}
ImageCharacteristics <- amin %>% filter(type=="Manual") %>% group_by(situation, bg, shotangle, detect) %>% dplyr::summarise(count=n())
ImageCharacteristics<-arrange(ImageCharacteristics, desc(count))
ImageCharacteristics<-ImageCharacteristics[1:5,]
knitr::kable(ImageCharacteristics, booktabs = TRUE, longtable=TRUE, format.args=list(width=8), caption="This table outlines the combinations of image attibutes that are most common in the image set. The combination of the Logo Wall background and the Player Shoulder Height angle are shared by three of the five image combinations.", format = "latex")
```

@@

# Acknowledgements

@@

# Supplementary material

>>>>

---
title: "Detecting Facial Expressions in Professional Tennis Matches"
author: "Stephanie Kobakian, Mitchell O'Hara-Wild, Dianne Cook, Stephanie Kovalchik"
date: "28 July 2017"
output: bookdown::pdf_document2
toc: false
fig_caption: yes
number_sections: false
fontsize: 11pt
documentclass: article
bibliography: references.bib
biblio-style: apalike
link-citations: true
---

@@

#Abstract {-}

@@

##Software selection

The choice of the initial software considered for this research was informed by a report that reviewed 'commercial off-the-shelf (COTS) solutions and related patents for face recognition in video surveillance applications.' [@Survey]

@@

To record the details of attributes for each face and scene a Shiny [@shiny] App was created. We called this Application our ManualClassificationProgram. This helped to provide information for all attributes quickly and consistently.

@@

```{r Image-Characteristics-Table, fig.cap ="\\label{tab:Image-Characteristics-Table}"}
ImageCharacteristics <- amin %>% filter(type=="Manual") %>% group_by(situation, bg, shotangle, detect) %>% dplyr::summarise(count=n())
ImageCharacteristics<-arrange(ImageCharacteristics, desc(count))
ImageCharacteristics<-ImageCharacteristics[1:5,]
knitr::kable(ImageCharacteristics, booktabs = TRUE, longtable=TRUE, format.args=list(width=8), caption="This table outlines the combinations of image attibutes that are most common in the image set. The combination of the Logo Wall background and the Level angle are shared by three of the five image combinations.", format = "latex")
```

@@

# Acknowledgements {-}

@@

# Supplementary material{-}
